%!TEX root = ../thesis.tex

\chapter*{\hfill\color{darkred}\hfill\pgfornament[anchor=center,width=3.6cm]{70}\color{black}{Acknowledgements}\hfill\color{darkred}\pgfornament[anchor=center,width=3.6cm]{70}\hfill}
%\begin{coverpage}{Acknowledgements}
    
    \epigraph{\itshape ``Yo soy yo y mi circunstancia, y si no la salvo a ella no me salvo yo'' \\ \scriptsize(``Ich bin ich und mein Lebensumstand, und wenn ich ihn nicht rette, dann rette ich auch mich nicht.'')}{--- J.~Ortega y Gasset, \textit{Meditaciones del Quijote (1914)}}

    This quote encapsulates the notion that self-understanding is deeply linked with an understanding of one's surroundings. As such, my journey here has been shaped not just by my own actions, but by the world around me. Consequently, \textbf{I am thankful to everyone I have ever shared a moment or space with}.

    Yet, there are some people I want to thank specifically, those who had a higher weight during my PhD journey (without any preferred order):
    \begin{itemize}
        \item I would like to thank my bachelor colleagues, especially: David Sánchez and Pedro J. Gea.
        \item Related to my university time, I would also thank my first research colleagues: Joaquín Berrocal, Fran Domínguez and Emilio Altozano.
        \item An especial mention to Manuel J. Gutiérrez, whom I initially met in Granada and later found again at \textsc{GSI}. Thanks for being a great training partner (when you could make it \faGrinWink[regular]), and for demonstrating passion for science and learning every day. You truly embody what a PostDoc should be. I wish you the best luck in your future, I am sure you will do great wherever you are.
        \item Thanks to my \textsc{GSI} colleagues. I truly enjoyed sharing my results (almost) \textbf{every} Wednesday, with RuiJiu Chen, Jan Glorius, Yuri Litvinov, Wolfram Korten, Shahab Sanjari and Sophia Dellmann. I thank Alex Gumberidze, Nikos Petridis, Sergiy Trotsenko and Shahab Sanjari for the (free \faGrinBeam[regular]) coffee breaks and the variety of topics we discussed, always with a funny note. I also thank the students who transitioned \textsc{KBW $3.029$} (my office) during this two and half years: George Hudson-Chang, Johannes Krempel-Hesse, Dima Dmytriiev, Ragan Sidhu, Maria Selina, Quanchao Song, among others.
        \item I thank the people I met during my two months in Orsay. Special mention to Jing, who picked my up at the Paris Bus Station after $9$ hours of bus with my bike, backpack, suitcase and a big bag. He showed me the area and even cooked some traditional delicious Chinese food. Following, I thank my Bulgarian friends Desi Kalaydjieva and Konstantin Stoychev. I really enjoyed our trip to Legnaro and surroundings. It would have been really boring without you.
        \item I thank Johanna Stachel for happily agreeing to act as the second referee of my thesis. It is a privilege to have such a distinguished researcher examine my work from a different perspective.
        \item Now is the turn for \textsc{Der Kalligraph von Kermanshah}, the supervisor in the shadows, my mentor+colleague+friend Shahab. You are an inspiration and motivation for any student, always with a smile, funny, charismatic, very thoughtful, intelligent and creative, without you \textsc{GSI} would not be the same. Thanks for everything \faGrinWink[regular]\faGrin*[regular].
        \item I would like to thank Klaus Blaum for welcoming me into his group as a PhD candidate, allowing me to conduct pioneering research, and enabling my doctoral studies at Heidelberg University. Thanks for your time and scientific advice throughout all these years, especially at the last stages of my PhD. 
        Moreover, thanks for the financial support and trust; any opportunity that I got, I could pursue without any doubt. I am still surprised that he is always the first one in answering any email, always with a concise and transparent message \faGrin*[regular]. He is an exceptional team leader, and he will continue to be.
        \item I thank Yuri A. Litvinov (I still have not discovered what the ``A.'' stands for) for providing the best working environment possible at \textsc{GSI}. I thank him for allowing me to conduct independent research, without never ever asking me to do anything outside the scope of my thesis. I also thank him for providing me with the best tools possible for working without questioning, and for his support, advice and expertise.
        \item I would also like to thank Wolfram Korten, for making the experiment possible, for pushing the theoreticians, and for keeping pursuing the nuclear two-photon decay. I have been in multiple experiments alongside Wolfram, all of them were successful, and I do not think it was a coincidence \faGrinWink[regular]. I enjoyed working together.
        \item Finally, I would like to thank the persons with the highest impact, my family. Querría agradecer a mi familia por todo su apoyo a lo largo de mi vida, dándome el lujo de estudiar sin ninguna preocupación. Gracias a mi papá (Paco), a mi mamá (Yolanda), y a mis hermanos Borja y Fran. Ich möchte mich auch bei meiner Schwiegerfamilie bedanken, dass sie mich in die Familie aufgenommen hat, insbesondere bei Lothar und Marlen.
        \item[\faHeart] Sophia, du bist das Beste, was mir je passiert ist. Vielen Dank für deine tägliche Unterstützung und Liebe. Neben dir fühle ich, dass ich glücklich strahlen kann, bis zum letzten Akt.
    \end{itemize}

%\end{coverpage}