%!TEX root = ../thesis.tex

\chapter*{List of Publications}
Parts of this work have been submitted to, and will be submitted to, various scientific journals.
Below is my list of publications and their corresponding usage within this thesis.

\subsection*{Utilized publications}
\begin{itemize}
    \item \underline{D.~Freire-Fernández}, \textit{et al.}, ``{\it Measurement of the Isolated Nuclear Two-Photon Decay in $^{72}\mathrm{Ge}$}'', under review in Physical Review Letters. A pre-printed version can be found under \href{https://doi.org/10.48550/arXiv.2312.11313}{10.48550/arXiv:2312.11313}. This latter version is cited as \cite{freirefernández2023measurement}.
    \begin{itemize}
      \item[O] Parts of the text, tables and figures of \cref{subsec:chap3:72gemeasurementenergy}, \cref{subsec:chap3:hl-twophoton} and \cref{sec:concl:conclusions} have been taken from \cite{freirefernández2023measurement}, as indicated in their first paragraph.
    \end{itemize} 
  \end{itemize}
\subsubsection*{Developed software packages}
\begin{itemize}
  \item \underline{D.~Freire-Fernández}, and G.~Hudson-Chang, ``{\it \textsc{RionID}: Collection of code for the identification of ringed ions in Python}'', Zenodo: \href{https://doi.org/10.5281/zenodo.8169342}{10.5281/zenodo.8169342}. Cited as \cite{rionid}.
  \begin{itemize}
    \item[O] This software was utilized for the ion identification (refer to \cref{subsubsec:chap2:rionid} and \cref{sec:chap3:identification}).
  \end{itemize}
  \item \underline{D.~Freire-Fernández}, ``{\it \textsc{TDMchopS}: A toolkit for automatic chopping of continuously acquired complex valued radio frequency samples}'', Zenodo: \href{https://doi.org/10.5281/zenodo.8172227}{10.5281/zenodo.8172227}. Cited as \cite{freire_fernandez_2023_8172227}. 
  \begin{itemize}
    \item[O] This software was used for the determination of the time of injection in the \textsc{NTCAP} data (refer to \cref{subsubsec:chap2:injectiontime}).
  \end{itemize}
\end{itemize}
All my software can be found in {\faGithub\ GitHub: \href{https://github.com/DFreireF}{@DFreireF} \par}
\subsection*{Manuscripts in preparation}
The following manuscripts are currently under preparation and will incorporate text, figures and tables from this thesis:
\begin{itemize}
  \item \underline{D.~Freire-Fernández}, \textit{et al.}, {\it ``First electron conversion factor measurements at storage rings''}, (in preparation). 
  \item \underline{D.~Freire-Fernández}, \textit{et al.}, ``{\it $B\rho$-allowed combined Schottky plus Isochronous Mass Spectrometry (\textsc{S+IMS})}'', (in preparation).
\end{itemize}
\subsection*{Non-used publications}
The following publications, to which I also contributed as a co-author, have not been used in this thesis:
\begin{itemize}
  \item M.~Sguazzin, \textit{et al.}, ``{\it First measurement of the neutron-emission probability with a surrogate reaction in inverse kinematics at a heavy-ion storage ring}'', under review in Physical Review Letters. The pre-print can be found under \href{https://doi.org/10.48550/arXiv.2312.13742}{10.48550/arXiv.2312.13742}.
  \item S.~F.~Dellmann, \textit{et al.}, ``{\it Proton capture on stored radioactive Te ions}''. \href{https://doi.org/10.1051/epjconf/202327911018}{EPJ Web of Conferences 279, 11018}.
  \item M.~Sguazzin, \textit{et al.}, ``{\it Indirect measurements of neutron-induced reaction crosssections at heavy-ion storage rings}''. \href{https://doi.org/10.1051/epjconf/202327911006}{EPJ Web of Conferences 279, 11006}.
\end{itemize}

All my past, present and future research will be found at: \orcidlink{0000-0002-5898-9291} \href{https://orcid.org/0000-0002-5898-9291}{https://orcid.org/0000-0002-5898-9291}.